### 2011-11-02 Text/introduction.tex
Double results are ready.

\section{Comparison between different approaches}
We consequently will examine different approaches to the mass transfer definition, Fig.
\ref{fig:comparison:one:unit:cell}:
\begin{description}
\item[I] Definition of \citet{vanbaten-circular} with periodic boundary conditions where a bubble
is located near the entrance of the computational domain, and the characteristic concentration is
the inlet/outlet concentration, Fig \ref{fig:benchmark}. 
\item[II] Definition of \citet{vanbaten-circular} with periodic boundary conditions where a
bubble is located in the middle of the computational domain, and the characteristic concentration
is the inlet/outlet concentration.
\item[III] Definition of \citet{vanbaten-circular} with periodic boundary conditions where a bubble
is located in the middle of the computational domain, and the characteristic concentration is the
average concentration.
\item[IV] Definition with the concentration jump between inlet and outlet over one unit cell.
\end{description}
\begin{figure}[htb!]
\includegraphics[width=\textwidth]{Figures/benchmark_periodic.eps}
\caption{The two-dimensional benchmarks for the hydrodynamics (top) and the mass transfer
coefficient (bottom). \label{fig:benchmark}}
\end{figure}

\begin{figure}[htb!]
\includegraphics[width=0.5\textwidth]{Figures/steady_state_per_entrance.eps}
\includegraphics[width=0.5\textwidth]{Figures/steady_state_per_aver.eps}\\
\includegraphics[width=0.5\textwidth]{Figures/steady_state_per_middle_outlet.eps}
\includegraphics[width=0.5\textwidth]{Figures/steady_state_jos_inlet_outlet.eps}\\
\caption{\label{fig:comparison:one:unit:cell}}
\end{figure}
All the comparison is summarized in Table \ref{table:one_unit_comparison}.
\begin{table}[htb!]
\begin{tabularx}{\textwidth}{|X|X|X|X|X|X|X|X|}
\hline
$Ca$&$Fo$&$\vol_{ent},\,\mathrm{s}^{-1}$&\\
\hline
$0.026$&$0.08493$&$0.2737$&$0.1692$&$0.2631$&$3.6756$\\
$0.047$&$0.02160$&$0.3664$&$0.2852$&$0.4553$&$11.4822$\\
$0.080$&$0.00588$&$0.4959$&$0.4079$&$0.6920$&$15.1964$\\
$0.065$&$0.00862$&$0.4734$&$0.4303$&$0.8923$&$21.4517$\\
$0.222$&$0.00103$&$0.8505$&$0.6109$&$0.8679$&N/A\\
$0.479$&$0.00034$&$1.1541$&$0.9884$&$1.2995$&N/A\\
$0.736$&$0.00018$&$1.1801$&$1.2199$&$1.1555$&N/A\\
$0.989$&$0.00012$&$1.2215$&$1.3400$&$1.0350$&N/A\\
\hline
\end{tabularx}
\caption{Simulation results for different capillary numbers.
\label{table:one_unit_comparison}}
\end{table}

>>>>

\section{Comparison between different approaches for one unit cell}
We consequently will examine different approaches to the mass transfer definition, Fig.
\ref{fig:comparison:one:unit:cell}:
\begin{description}
\item[I] Definition of \citet{vanbaten-circular} with periodic boundary conditions where a bubble
is located near the entrance of the computational domain, and the characteristic concentration is
the inlet/outlet concentration, Fig \ref{fig:benchmark}. 
\item[II] Definition of \citet{vanbaten-circular} with periodic boundary conditions where a bubble
is located near the entrance of the computational domain, and the characteristic concentration is
the average concentration, Fig \ref{fig:benchmark}.
\item[III] Definition of \citet{vanbaten-circular} with periodic boundary conditions where a
bubble is located in the middle of the computational domain, and the characteristic concentration
is the inlet/outlet concentration.
\item[IV] Definition of \citet{vanbaten-circular} with periodic boundary conditions where a bubble
is located in the middle of the computational domain, and the characteristic concentration is the
average concentration.
\item[V] Definition with the concentration jump between inlet and outlet over one unit cell.
\end{description}
\begin{figure}[htb!]
\includegraphics[width=\textwidth]{Figures/benchmark_periodic.eps}\\
\includegraphics[width=\textwidth]{Figures/benchmark_middle.eps}\\
\caption{The two-dimensional benchmarks for the  the mass transfer
coefficient (bottom) for the bubble located near the entrance (top) and at the middle of the domain
(bottom). \label{fig:benchmark}}
\end{figure}

\begin{figure}[htb!]
\includegraphics[width=0.5\textwidth]{Figures/steady_state_per_entrance.eps}
\includegraphics[width=0.5\textwidth]{Figures/steady_state_inlet_aver.eps}\\
\includegraphics[width=0.5\textwidth]{Figures/steady_state_per_aver.eps}
\includegraphics[width=0.5\textwidth]{Figures/steady_state_per_middle_outlet.eps}\\
\includegraphics[width=0.5\textwidth]{Figures/steady_state_jos_inlet_outlet.eps}\\
\caption{\label{fig:comparison:one:unit:cell}}
\end{figure}
All the comparison is summarized in Table \ref{table:one_unit_comparison}.
\begin{table}[htb!]
\begin{tabularx}{\textwidth}{|X|X|X|X|X|X|X|X|}
\hline
$Ca$&$Fo$&$\vol_{ent},\,\mathrm{s}^{-1}$&$\vol_{aver},\,\mathrm{s}^{-1}$&$\vol_{mid,
aver},\,\mathrm{s} ^ { -1 }$&$\vol_{mid,out},\,\mathrm{s}^{-1}$&$\vol_{open},\,\mathrm{s}^{-1}$ \\
\hline
$0.026$&$0.08493$&$0.2737$&$0.1775$&$0.1692$&$0.2631$&$3.6756$\\
$0.047$&$0.02160$&$0.3664$&$0.3431$&$0.2852$&$0.4553$&$11.4822$\\
$0.080$&$0.00588$&$0.4959$&$0.4185$&$0.4079$&$0.6920$&$15.1964$\\
$0.065$&$0.00862$&$0.4734$&$0.4517$&$0.4303$&$0.8923$&$21.4517$\\
$0.222$&$0.00103$&$0.8505$&$0.6799$&$0.6109$&$0.8679$&N/A\\
$0.479$&$0.00034$&$1.1541$&$1.0460$&$0.9884$&$1.2995$&N/A\\
$0.736$&$0.00018$&$1.1801$&$1.2395$&$1.2199$&$1.1555$&N/A\\
$0.989$&$0.00012$&$1.2215$&$1.3493$&$1.3400$&$1.0350$&N/A\\
\hline
\end{tabularx}
\caption{Simulation results for different capillary numbers.
\label{table:one_unit_comparison}}
\end{table}
One can see that the only consistent result is for simulations which take into the account average
concentration. The results come to the steady-state after $1,000,000$ iterations. However, to
understand properly what is the real mass transfer coefficient one needs to perform a few units
simultions.

\section{Two unit cells results}
As far as one needs to restore the continuous picture one needs to make a simulation of a few
cells. This section provides results for two units. The results are summarized in Table
\ref{table:two_units}. The results for two sections are presented in Fig. \ref{fig:results:double}.
\begin{figure}[htb!]
\includegraphics[width=0.5\textwidth]{Figures/steady_double_overall.eps}
\includegraphics[width=0.5\textwidth]{Figures/steady_double_first.eps}\\
\includegraphics[width=0.5\textwidth]{Figures/steady_double_second.eps}
\caption{Overall mass transfer coefficient (top left), first part (top
right), second part (bottom left).\label{fig:results:double}}
\end{figure}
\begin{table}[htb!]
\begin{tabularx}{\textwidth}{|X|X|X|}
$0.7392$&$1.0564$&$0.4220$\\
$1.8993$&$2.8301$&$0.9684$\\
$3.3925$&$4.7522$&$2.0328$\\
$3.7870$&$4.5615$&$3.0125$\\
\end{tabularx}
\caption{Simulation results. \label{table:two_units}}
\end{table}
